\Title

### 2020-02-17 manuscript/manuscript.tex
Minor text improvement

The chosen distribution of sources should reproduce the measured data on the
survey points and simultaneously be able to make accurate
predictions of the measured harmonic field on non observed locations.

>>>>

The chosen distribution of sources should simultaneously reproduce the measured
data on the survey points and be able to make accurate predictions of the
measured harmonic field on non observed locations.
